The limits of self commitment and private paternalism \thanks{}

### 2022-07-15 donde.tex
change scheme in figures
tot vs tut inference analysis

This is not the first paper to find low demand for commitment, however it is the first we know of that can compare choice vs forcing with a money-metric outcome such as loan repayment. The fact that the Forced Commitment contract lowers financial costs for almost all clients, together with the fact that only 11\% choose it must mean that many consumers are choosing contracts with higher financial costs for themselves. We now use several different techniques to shed further light on the idea that the `wrong' people are choosing commitment.

Our core impacts show that forced commitment is uniquely effective, a result that can only arise if those who would not have freely chosen commitment benefit from it.  We now delve more deeply into this result.

\subsection{Treatment Effects for Compliers and Non-Compliers}

A unique feature of our design is the randomized assignment to treatment, control, and choice of treatment.  This structure allows us to observe the average value of both the treated and untreated potential outcomes, as well as the selection into treatment that would occur under choice.  A starting point for how to exploit this structure is to apply the logic usually used to estimate the Treatment on the Treated (ToT) to also recover the Treatment on the Untreated (TuT).  This approach assumes nothing about the decision to choose (other than random sampling generating counterfactual compliance rates that would have been the same in every arm), but imposes three exclusion restriction-style assumptions typical of Local Average Treatment Effect (LATE) analysis.  Namely, a) the typical assumption that an individual not choosing the treatment has the same potential outcome as one not offered it, then b) the mirror image assumption for the Forcing arm that an individual forced to take Commitment has the same potential outcome as an individual freely choosing it, and c) no spillovers from chooser to non-choosers in the choice arm.\footnote{\hl{For robustness we also try a Manski-type monotone IV approach with similar results.}}

More formally, let $Z_i$ be the observed, randomly assigned experimental allocation, where $Z_i=0$ denotes the control arm, $Z_i=1$ denotes the Forced arm, and $Z_i=2$ is the Choice arm.  Let $C_i$ be the choice type; $C_i=0$ when individual $i$ does not choose commitment and $C_i=1$ when chooses commitment, observed in the Choice arm and latent in the other two arms.  A fraction $p$ of individuals chooses the treatment in the Choice arm.  Finally, $D_i = Z_i\times \mathds{1}(Z_i\neq 2) + C_i\times \mathds{1}(Z_i=2)$ is the observed treatment indicator, and $Y(d,z)$ is the potential outcome function for $d=0,1$, and $z=0,1,2$.

To test the difference between gains for choosers versus gains from non-choosers we need to identify $\mathbb{E}[Y_1-Y_0\;|\;C=1]$ (the Treatment on the Treated), and $\mathbb{E}[Y_1-Y_0\;|\;C=0]$ (the Treatment on the Untreated).   The observed outcome in the Choice arm is the weighted average of the treated and untreated outcomes; $p \times\mathbb{E}[Y_1\;|\;C=1] + (1-p)\times\mathbb{E}[Y_0\;|\;C=0]$.  Given assumptions a) and c) above we can recover the ToT from the difference between the Choice and Control arms as is standard, and then symmetrically we can invoke b) and c) to recover the TuT from the difference between the Forced and Choice arms as follows:

\begin{align*}
ToT \equiv \mathbb{E}[Y_1 - Y_0 \;\mid\; C=1]  &=   \frac{\mathbb{E}[Y \;\mid\; Z=2] - \mathbb{E}[Y \;\mid\; Z=0]}{p} \\
TuT \equiv \mathbb{E}[Y_1 - Y_0 \;\mid \;C=0]  &=  \frac{\mathbb{E}[Y \;\mid\; Z=1] - \mathbb{E}[Y \;\mid\; Z=2]}{(1-p)} 
\end{align*}

This estimate of the ToT is the standard one that would result from instrumenting for compliance with the offering of treatment as in \cite{angrist1996identification}.  The TuT is the analogous estimator, which could be recovered in a regression pooling the forced and choice arms and instrumenting for \textit{not} complying with being assigned to the choice arm (for a more formal development, see the appendix).  The advantage of representing the estimands via division of the relevant ITT by the compliance (non-compliance) rate is that it allows us to estimate all the necessary terms from the single pooled regression Equation \ref{basic_reg}, from which the significance levels for the ToT, the TuT, and the difference between them can all be estimated as single-equation F-tests:

\[ToT = \frac{\beta^C}{p}; \qquad\quad TuT = \frac{(\beta^F - \beta^C)}{(1-p)}; \qquad\quad (ToT-TuT) = \frac{\beta^C}{p}- \frac{(\beta^F - \beta^C)}{(1-p)}. \]

@@

@@

@@

>>>>

\todo[inline]{Issac: At different points in the paper we use different conventions for whether a positive treatment effect is ``good'' or ``bad.'' We should pick one and stick with it throught to avoid confusion. (E.g. ToT/TuT tables treat positive as good but figure 15 treats negative as good.)}

\todo[inline]{Think more carefully about the ``mistake'' wording here. There's a difference between an ex-ante mistake and an ex-post mistake. Need to think more carefully about this. This also relates to the question about what information to use in the first machine learning exercise. I think if we use the $\text{ATE}(X)$ that's closer to an ex ante measure than if we use, say, $\mathbm{E}[Y_1|X] - Y_0$.}

This is not the first paper to find low demand for commitment, however it is the first we know of that can compare choice versus forcing with a money-metric outcome such as loan repayment. As discussed above, a policy of forced commitment substantially lowers financial costs on average, both compared to a baseline no-commitment contract and a policy in which borrowers are free to choose their preferred contract. In spite of this, only 11\% of those in the choice arm choose commitment. In a world of heterogeneous treatment effects, this could nevertheless be consistent with individual rationality. So do the the other 89\% know something about their personal situations that we as researchers do not, or are most people in the choice arm making a costly mistake? We now present a range of econometric exercises that shed light on this question. Taken together, they cast considerable doubt on the notion of ``selection on gains,'' as embodied in the traditional Roy model. While we find evidence of substantial treatment effect heterogeneity, most borrowers would experience lower financial costs under a commitment contract. Indeed, leveraging a unique feature of our experimental design, we show that the average effect of commitment for the \emph{untreated}, those who would not voluntarily choose commitment, is large and negative. In an important sense the ``wrong'' people are choosing commitment.

\subsection{Potential Outcomes and Exclusion}

To interpret our evidence on the importance of paternalism presented below, it is important to be precise about the potential outcomes in our empirical setting. This requires introducing some notation. Let $Z_i \in \{0, 1, 2\}$ denote the treatment arm to which to participant $i$ was assigned: $Z_i = 0$ denotes the forced no-commitment arm, $Z_i = 1$ denotes the forced commitment arm, and $Z_i = 2$ denotes the choice arm. Now let $D_i$ be the treatment that participant $i$ actually \emph{received}, where $D_i = 0$ denotes no-commitment and $D_i = 1$ denotes commitment. By design, our experiment features perfect compliance in the $Z_i = 0$ and $Z_i = 1$ arms. It is only in the $Z_i = 2$ arm that participants are free to choose between alternative contracts. Let $C_i \in \{0, 1 \}$ denote a participant's ``choice type.'' If $C_i = 1$ then participant $i$ \emph{would choose commitment}, given the choice; if $C_i = 0$ she would not. Whereas a participant's choice type $C_i$ is only observed if she is allocated to the choice arm ($Z_i = 2$), her treatment $D_i$ and experimental arm $Z_i$ are always observed. Given the design of our experiment, these quantities are related by
\begin{equation}
D_i = \mathbbm{1}(Z_i \neq 2) Z_i + \mathbbm{1}(Z_i = 2) C_i.
\label{eq:potentialTreatments}
\end{equation}

We maintain the stable unit treatment value assumption (SUTVA) throughout. This means that participant $i$'s outcomes depend only on her \emph{own} values of $Z_i$ and $D_i$, not those of any other person in the experiment: there are no \emph{spillovers}. Under this assumption, a fully general model for the potential outcomes in our experiment would take the form $Y_i(d, z)$ for $d\in \{0,1\}$ and $z \in \{0, 1, 2\}$, allowing participant $i$'s potential outcome to depend \emph{both} on the treatment she actually receives, $D_i$, and the experimental arm to which she is assigned, $Z_i$. This model is too general, however, to allow us to explore the importance of paternalism. Accordingly, we impose the following standard exclusion restriction:
\begin{equation}
Y_i(d=0, z=0) = Y_i(d=0, z=2) \equiv Y_{i0}, \quad
Y_i(d=1, z=1) = Y_i(d=1, z=2) \equiv Y_{i1}.
\label{eq:exclusion}
\end{equation}
\Eqref{eq:exclusion} says that each participant's potential outcome is the same regardless of whether she \emph{chooses} a particular treatment $D=d$ or is \emph{assigned} the same treatment. Viewing $Z_i$ as an instrumental variable (IV) for the treatment $D_i$, this nothing more than the usual IV exclusion restriction.\footnote{\cite{chamberlain2011bayesian} uses an identical assumption to develop a theory of optimal treatment choice for an individual who has access to data from an RCT.} \Eqref{eq:exclusion} is plausible in our empirical setting and has testable implications that we fail to reject: see Appendix \todo{Fill in}{???} for details. Under \eqref{eq:exclusion}, each participant's observed outcome $Y_i$ is related to her potential outcomes $(Y_{i0}, Y_{i1})$ according to 
\todo[inline]{Issac: add a section \ref{bound_tot_tut_appendix} to the appendix and drop in the results for the Huber \& Mellace stuff; Frank: follow-up and draft that section of the appendix.}
\begin{equation}
    Y_i = \mathbbm{1}(Z_i =0) Y_{i0} + \mathbbm{1}(Z_i = 1)  Y_{i1}  + \mathbbm{1}(Z_i = 2) \left[(1 - C_i) Y_{i0} + C_i Y_{i1} \right].
\label{eq:potentialOutcomes}
\end{equation}

\Eqref{eq:potentialOutcomes} is the key to understanding the results that follows. By randomly assigning $Z_i=0$ and $Z_i = 1$, our experiment identifies the marginal distributions of $Y_{i0}$ and $Y_{i1}$ in the population as a whole. By randomly assigning $Z_i=2$, it likewise identifies the share of people with $C_i = 1$ (the treated), the distribution of $Y_{i1}$ for these individuals, and the distribution of $Y_{i0}$ for those with $C_i = 0$ (the untreated). Because $Z_i$ is assigned independently of pre-treatment covariates $X_i$, our design also identifies the corresponding \emph{conditional} distributions of $Y_{i0}$ and $Y_{i1}$ given $X_i$. These distributions are the ingredients that we use below to explore the importance of paternalism.

%The fact that the Forced Commitment contract lowers financial costs for almost all clients, together with the fact that only 11\% choose it must mean that many consumers are choosing contracts with higher financial costs for themselves. We now use several different techniques to shed further light on the idea that the `wrong' people are choosing commitment.

%Our core impacts show that forced commitment is uniquely effective, a result that can only arise if those who would not have freely chosen commitment benefit from it.  We now delve more deeply into this result.

\subsection{Treatment Effect Heterogeneity}
\todo[inline]{There's a connection between homogeneous treatment effects and predictability. In a homogeneous world, the treatment effect is perfectly predictable from the ATE.}

If the effect of commitment were homogeneous, there would be nothing more to say on the topic of paternalism. Our estimates of $\mathbbm{E}(Y_{i1} - Y_{i0}) = \mathbbm{E}(Y_i|Z_i=1) - \mathbbm{E}(Y_i|Z_i=0)$ presented above are large and statistically significant. If $\Delta_i \equiv Y_{i1} - Y_{i0}$ were constant across $i$, this would be enough to conclude that the 89\% who do not choose commitment would have been better off if they had. As we now show, however, the effect of commitment varies considerably across individuals. Our approach relies on the following simple observation: if $\Delta_i$ is constant across $i$ then we must have 
\[
\text{ATE}(X_i) \equiv \mathbbm{E}[\Delta_i |X_i] = \mathbbm{E}[\Delta_i] \equiv \text{ATE}
\]
for any covariates $X_i$ that vary across $i$. If, on the other hand, $\text{ATE}(X_i)$ can be predicted using some scalar function $\tau(\cdot)$ of $X_i$, then the average treatment effect function is not constant so there must be treatment effect heterogeneity.

We operationalize this idea using a two-step approach proposed by \cite{chernozhukov2018generic}.  We begin by randomly dividing the participants in the forced arms of the experiment ($Z_i \neq 2$) into two groups: a ``training set'' and a \todo{80/20 split?}{``test set.''} In the first step, we apply random forests to the training set to estimate two proxy predictors: $\psi(\cdot|\text{Training})$ approximates the untreated potential outcome function, $\mathbbm{E}[Y_{i0}|X_i] = \mathbbm{E}[Y_i|Z_i=0,X_i]$, while  $\tau(\cdot|\text{Training})$, approximates the average treatment effect function
\[
\text{ATE}(X_i) = \mathbbm{E}[Y_i|Z_i=1,X_i] - \mathbbm{E}[Y_i|Z_i=0, X_i].
\]
The proxy predictors need not be unbiased or even consistent estimators of the functions they aim to approximate: the goal of this exercise is merely to find a scalar function of $X_i$ that \emph{accurately predicts} $\text{ATE}(X_i)$.

In the second step we fit a linear regression model to data from the training set using regressors constructed from the proxy functions $\psi(\cdot|\text{Training})$ and $\tau(\cdot|\text{Training})$ constructed in the first step. In particular, we estimate 
\begin{equation}
Y_i = \alpha_0 + \alpha_1 \psi_i + \beta_1 (Z_i - \mathbbm{E}[Z_i]) + \beta_2 (Z_i - \mathbbm{E}[Z_i])(\tau_i - \mathbbm{E}[\tau_i]) + \epsilon_i
\label{eq:chernreg}
\end{equation}
where $\psi_i \equiv \psi(X_i|\text{Training})$ and $\tau_i \equiv \tau(X_i|\text{Training})$.\footnote{This is a slightly simpler regression than the one proposed in equation (3.1) of \cite{chernozhukov2018generic}, which involves propensity score weights. Because the random assignment of $Z$ in our experiment does \emph{not} condition on $X$, the propensity score weights in our case are constant over $X$ and hence drop out.} As shown by \cite{chernozhukov2018generic}, the coefficients $\beta_1$ and $\beta_2$ from \eqref{eq:chernreg} identify the \emph{best linear predictor} of the conditional ATE based on $\tau(\cdot|\text{Training})$, namely
\[
\beta_1 = \mathbbm{E}[\text{ATE}(X_i)] = \text{ATE}, \quad
\beta_2 = \frac{\text{Cov}[\text{ATE}(X_i), \tau_i]}{\text{Var}(\tau_i)}.
\]
If treatment effects are homogeneous we must have $\beta_2 = 0$. Rejecting this hypothesis establishes that $\tau_i$ predicts $\text{ATE}(X_i)$ and hence that $\Delta_i$ varies. Since $\tau_i$ and $\psi_i$ do not depend on the test set, inference for the regression in \eqref{eq:chernreg} is straightforward conditional on the Training/Test split.

\todo[inline]{Discuss the results here.}

\todo[inline]{Issac: re-run this exercise with removing the propensity score weights $p(Z)$. Presumably it shouldn't change anything, but it's simpler to explain what we do and probably less noisy

\begin{table}[H]
\begin{center}
\scriptsize{\input{./Tables/test_calibration_2.tex}}
\end{center}
\end{table}

}

\todo[inline]{Some Questions for Issac: (1) How are we carrying out the sample splitting? If we cluster standard errors at the branch-day level, we should take this into account when we split. (2) How are you carrying out inference for $\beta_2$? Chernozhukov et al discuss two approaches: ``conditional'' and ``variational.'' The former is simpler as it conditions on the training/test split. The latter is a bit more involved, since one accounts for uncertainty arising from different splits. (3) What are the details of the random forest procedure employed here? (Tuning parameters choice, etc.) We should put them into the appendix.}

\subsection{Bounding the Distribution of Treatment Effects}

As explained above, our experimental design identifies the marginal distributions of $Y_{i0}$ and $Y_{i1}$, call them $F_0$ and $F_1$. We can estimate them using the empirical CDF of $Y_i$ for $Z_i=0$ and $Z_i = 1$ respectively. Because we can never observe both treated and untreated potential outcomes for the same person, however, the distribution $F_\Delta$ of the individual treatment effects $\Delta_i \equiv Y_{i1} - Y_{i0}$ cannot be identified. It can, however, be bounded. \cite{fan2010sharp} show that the best possible pointwise bounds for $F_\Delta$ are given by $\underline{F}(\delta) \leq F_\Delta(\delta) \leq \overline{F}(\delta)$ where the bounding functions $\underline{F}$ and $\overline{F}$ are defined as 
\[
\underline{F}(\delta) \equiv \max \left\{0, \sup_y F_1(y) - F_0(y - \delta)  \right\}, \quad
\overline{F}(\delta) \equiv 1 + \min \left\{0, \inf_y F_1(y) - F_0(y-\delta) \right\}.
\]
These bounds are simple to compute, and can be surprisingly informative. Here we use them to bound the fraction of borrowers who benefit from commitment. Given the way that we have defined our outcome variables, this is the share of borrowers whose treatment effect is \emph{negative}, i.e.\ $F_\Delta(0)$. To construct the sharp bounds for this quantity, we simply substitute $\delta = 0$ into the preceding equations and estimate $F_0$ and $F_1$ using their empirical analogues constructed from the forced commitment and forced no-commitment arms of the experiment.

\todo[inline]{Issac: add in the confidence interval at $\delta = 0$ along with the figure \ref{fan_park_bounds}; Frank follow-up to add 1-2 sentences discussing the results. Presumably we find that $F_\Delta(0) > 0.11$ this means that at least some people who choose not to commit \emph{must} be making a mistake, although we don't know who they are and this doesn't tell us how large the mistake is.}

An alternative way of presenting the \cite{fan2010sharp} bounds is in terms of quantiles of the distribution of $\Delta$. Let $0 < q < 1$, and define $Q_0, Q_1, Q$ to be the quantile functions corresponding to $F_0, F_1$ and $F_\Delta$.\footnote{In other words, $Q_0(q) \equiv \inf \{x | F(x) \geq q\}$ and so on.} Then the sharp bound for $Q_\Delta(q)$ is given by $\underline{Q}(q) \leq Q(q) \leq \overline{Q}(q)$ where
\[
\overline{Q}(q) \equiv \inf_{u \in [q,1]} [Q_1(u) - Q_0(u - q)], \quad
\underline{Q}(q) \equiv \sup_{u\in [0,q]} [Q_1(u) - Q_0(1 + u - q)]
\]
By substituting $q = 0.11$, these expressions allow us to bound the 11th percentile of the distribution of $\Delta$. Under a stylized Roy model in which borrowers with the largest (negative) treatment effects choose commitment, $Q(0.11)$ equals the treatment effect for the borrower at the margin of indifference between choosing commitment.

\todo[inline]{Issac: add the interval for $Q(0.11)$. Maybe we don't need a second figure with the confidence bands for the whole quantile function. (Overkill?) Frank: add a sentence or two discussing the results. Presumably the aforementioned quantile is indeed negative and fairly large.}

Taken together, these bounds suggest that at least some borrowers who would benefit from commitment do not choose it when offered.

\subsection{Treatment on the Treated and Untreated}
In the preceding section, we used outcome data from the forced arms ($Z_i\neq 2$) along with the commitment take-up rate in the choice arm ($Z_i = 2$) to argue that at least some of the 89\% of participants who did \emph{not} choose commitment would have been better off if they had. By additionally examining \emph{outcome data} in the choice arm, it is possible to say more. We now show how our experimental design can be used to identify the average effect of commitment for both those who would choose it (the treated) and those who would not (the untreated). In particular, we identify the treatment on the treated (ToT) and treatment on the untreated (TuT) effects, defined as follows:
\[
\text{ToT} \equiv \mathbbm{E}(Y_{i1} - Y_{i0} | C_i = 1), \quad
\text{TuT} \equiv \mathbbm{E}(Y_{i1} - Y_{i0} | C_i = 0).
\]
The TuT and ToT effects are particularly interesting for understanding the importance of paternalism. If the TuT is positive, this means that someone who did not choose commitment would have been experienced a better outcome \emph{on average} if she had. In a canonical Roy model, the ToT should exceed both the TuT and average treatment effect (ATE). Because our design identifies all three quantities, it allows us to test this implication directly. If the ToT is statistically distinguishable from and substantially larger than the TuT, this provides empirical support for the relevance of selection-on-gains in real-world decision-making.

A number of recent papers compare estimates of the ToT and TuT to better understand who selects into treatment and why, e.g.\ \cite{cornelissen2018benefits} and \cite{Walters}. While valuable and interesting, this line of work relies, at least to some extent, upon structural modeling assumptions to extrapolate from the reduced-form quantities that are identified by the data alone to more interesting, and economically relevant, causal parameters.\footnote{While the marginal treatment effects (MTE) approach \citep{heckman2007econometric} can in principle be used to identify the ToT and TuT without parametric restrictions, doing so requires an instrumental variable $Z$ with sufficiently rich support that the probability of treatment take-up given $Z$ varies continuously between zero and one. In practice, instrumental variables are usually discrete and, even when continuous, typically have a more modest effect on take-up.} An alternative approach aims to avoid structural assumptions by calculating conditional local average treatment effects (LATE) given observed covariates $X$ and reweighting these according to the distribution of $X$ in some population of interest \citep{aronow2013beyond,angrist2013extrapolate}. For example, one might re-weight using the distribution of $X$ in the population as a whole, rather than the sub-population of compliers, to extrapolate from LATE to ATE. But you can't squeeze blood from a stone. This ``LATE-and-reweight'' approach relies upon assumptions of its own, most crucially the assumption that there is \emph{no selection-on-gains} conditional on $X$, i.e.\ that the conditional LATE equals the conditional ATE. As far as we are aware, ours is the only paper in the literature to identify the ToT and TuT without ruling out unobserved selection-on-gains or relying on additional structural modeling assumptions. This is possible because of the unique design of our experiment.

\todo[inline]{Presumably we want to say something about this design potentially being applicable to other settings?}

The key insight can be read directly from \eqref{eq:potentialTreatments} and \eqref{eq:potentialOutcomes}. Viewing $Z_i$ as an instrumental variable, our design can be interpreted as a \emph{pair} of RCTs, each subject to one-sided non-compliance.\footnote{For a full derivation, see Appendix ???.} The first of these compares $Z_i=0$ to $Z_i = 2$. For each individual with $Z_i = 0$ we have $D_i = 0$ and observe $Y_{i0}$. For those with $Z_i = 2$ we have $D_i = C_i$ and observe $(1 - C_i) Y_{i0} + C_i Y_{i1}$. This is identical to a ``randomized encouragement'' design in which treatment is only available to those who are encouraged: $Z_i = 2$. Under this interpretation, those with $C_i = 1$ are ``the compliers'' and it follows that 
\begin{equation}
\frac{\mathbbm{E}(Y_i|Z_i=2) - \mathbbm{E}(Y_i|Z_i =0)}{\mathbbm{E}(D_i|Z_i=2)-\mathbbm{E}(D_i|Z_i=0)} = 
\frac{\mathbbm{E}(Y_i|Z_i=2) - \mathbbm{E}(Y_i|Z_i =0)}{\mathbbm{E}(D_i|Z_i=2)} = \mathbbm{E}(Y_{i1} - Y_{i0}|C_i = 1)
\label{eq:ToT}
\end{equation}
since $\mathbbm{E}(D_i|Z_i=0)=0$ by \eqref{eq:potentialTreatments}.

A closely related if slightly less intuitive argument can be used to construct a Wald estimand that identifies the TuT. Here we consider $Z_i = 1$ to be the ``encouragement'' and compare the outcomes for these individuals to those with $Z_i = 2$. If $Z_i = 1$ then $D_i = 1$ and we observe $Y_{i1}$; If $Z_i = 2$ then $D_i = C_i$ and we observe $(1 - C_i) Y_{i0} + C_i Y_{i1}$. Again, we can view this as an experiment with one-sided non-compliance, but now the situation is reversed. Everyone with $Z_i = 1$ is treated, but some people with $Z_i = 2$ are ``always-takers'' who obtain the treatment ($D_i = 1$) despite having been allocated to the ``control'' arm $Z_i=2$. Under this interpretation, the ``compliers'' are those with $C_i = 0$: when $Z_i=1$ they take the treatment, and when $Z_i=2$, they do not. Thus, 
\begin{equation}
\frac{\mathbbm{E}(Y_i|Z_i=1) - \mathbbm{E}(Y_i|Z_i =2)}{\mathbbm{E}(D_i|Z_i=1)-\mathbbm{E}(D_i|Z_i=2)} = 
\frac{\mathbbm{E}(Y_i|Z_i=1) - \mathbbm{E}(Y_i|Z_i =0)}{1 - \mathbbm{E}(D_i|Z_i=2)} = \mathbbm{E}(Y_{i1} - Y_{i0} | C_i = 0)
\label{eq:TuT}
\end{equation}
since $\mathbbm{E}(D_i|Z_i = 1)= 1$ by \eqref{eq:potentialTreatments}.

\Eqref{eq:ToT} and \eqref{eq:TuT} are useful for understanding why our design identifies the ToT and TuT, but they are less convenient for estimation and inference. In Appendix \todo{Frank: fill in}{???}, we show that
\begin{align}
\label{eq:ToTreg}
Y_i &= \mathbbm{E}(Y_{i0}) + (\text{ATE}) \mathbbm{1}(Z_i = 1) + (\text{ToT}) \left[\mathbbm{1}(Z_i = 2) \times D_i\right] + U_i \\
\label{eq:TuTreg}
Y_i &= \mathbbm{E}(Y_{i1}) + (\text{ATE}) \left[ -\mathbbm{1}(Z_i = 0)\right] + (\text{TuT}) \left[ -\mathbbm{1}(Z_i = 2) \times (1 - D_i)\right] + V_i 
\end{align}
where the error terms $U_i$ and $V_i$ satisfy 
\[
\mathbbm{E}(V_i) = \mathbbm{E}(U_i) = \mathbbm{E}[U_i \mathbbm{1}(Z_i = z)] = \mathbbm{E}[V_i \mathbbm{1}(Z_i = z)] = 0, \quad z = 0, 1, 2.
\]
It follows that a pair of just-identified, linear instrumental variables regressions can be used to estimate and carry out inference for each of our quantities of interest. To identify the ATE and ToT, run IV on \eqref{eq:ToTreg} with instruments $\mathbbm{1}(Z_i = 1)$ and $\mathbbm{1}(Z_i=2)$. An F-test based on this regression can then be used to test the restriction $\text{ATE} = \text{ToT}$, and the usual IV output can be used to carry out inference for the ToT. No programming is required. Similarly, to identify the ATE and TuT run IV on \ref{eq:TuTreg} with instruments $\mathbbm{1}(Z_i = 0)$ and $\mathbbm{1}(Z_i = 2)$. An F-test based on this regression can then be used to test the restriction $\text{ATE} = \text{TuT}$, and the usual IV output can be used to carry out inference for the TuT. Again, no programming or special software is required.

As explained above, a canonical Roy model would suggest that $\text{TuT} \leq \text{ATE} \leq \text{ToT}$. For this reason it is particularly interesting to consider inference for the \emph{difference} $(\text{ToT} - \text{TuT})$. The point estimate of this difference can be constructed directly from the results of the IV regressions described above. Because the respective estimates appear in different equations, however, a bit more work is required to obtain a standard error for $(\text{ToT} - \text{TuT})$. Define the shorthand
\[
p_0 \equiv \mathbbm{P}(Z_i=0), \quad p_1 \equiv \mathbbm{P}(Z_i = 1), \quad q_0 \equiv \mathbbm{E}[\mathbbm{1}(Z_i = 2)(1 - D_i)], \quad q_1 \equiv \mathbbm{E}[\mathbbm{1}(Z_i = 2) D_i].
\]
As shown in Appendix \todo{Frank: fill in}{???}, the asymptotic variance of $(\text{Tot} - \text{TuT})$ is given by
\[
\text{AVAR}(\text{ToT} - \text{TuT}) = \boldsymbol{\omega}' \boldsymbol{\Sigma} \boldsymbol{\omega}, \quad
\boldsymbol{\omega}' \equiv \displaystyle \begin{bmatrix}
-\frac{1}{q_1} & \frac{1}{q_0} & \left(\frac{p_1 - 1}{p_0q_1} - \frac{1}{q_0}\right) & -\frac{1}{q_1} - \frac{1 - p_0}{p_1 q_0}
\end{bmatrix}
\]
where $\boldsymbol{\Sigma}$ is a covariance matrix that can be estimated from the residuals of \eqref{eq:ToTreg} and \eqref{eq:TuTreg}. Under iid observations,

\todo[inline]{Explain two leading forms that $\Sigma$ can take: heterosked and cluster}

\todo[inline]{Frank: give an overview of how to do the comparison of TuT and ToT. Want it to be ``idiot proof'' -- easy to do in standard software, etc. Details in the appendix but want the contribution to be clear. Cluster at the level of the randomization. (Almost WLOG for experiments). Can put some additional details in the appendix.}

\todo[inline]{Issac: add the table of TuT/ATE/ToT results without covariates. For the moment I suppose we \emph{don't} have the ToT/TuT comparison. (See Frank todo above!)}

\todo[inline]{Because they appear in different equations, testing TuT = ToT is slightly more involved. Explain how to do it here, but put additional details in the appendix.}

\todo[inline]{Frank: after the preceding todo notes, revise the text below that discusses the ToT/TuT etc results. Think about how to compare/contrast/relate to the bounding exercises above as well as the ITT results.}

%A unique feature of our design is the randomized assignment to treatment (forced commitment), control (forced no-commitment), and choice of treatment.

%This structure allows us to observe the average value of both the treated and untreated potential outcomes, as well as the selection into treatment that would occur under choice.  A starting point for how to exploit this structure is to apply the logic usually used to estimate the Treatment on the Treated (ToT) to also recover the Treatment on the Untreated (TuT).  This approach assumes nothing about the decision to choose (other than random sampling generating counterfactual compliance rates that would have been the same in every arm), but imposes three exclusion restriction-style assumptions typical of Local Average Treatment Effect (LATE) analysis.  Namely, a) the typical assumption that an individual not choosing the treatment has the same potential outcome as one not offered it, then b) the mirror image assumption for the Forcing arm that an individual forced to take Commitment has the same potential outcome as an individual freely choosing it, and c) no spillovers from chooser to non-choosers in the choice arm.\footnote{\hl{For robustness we also try a Manski-type monotone IV approach with similar results.}}

%More formally, let $Z_i$ be the observed, randomly assigned experimental allocation, where $Z_i=0$ denotes the control arm, $Z_i=1$ denotes the Forced arm, and $Z_i=2$ is the Choice arm.  Let $C_i$ be the choice type; $C_i=0$ when individual $i$ does not choose commitment and $C_i=1$ when chooses commitment, observed in the Choice arm and latent in the other two arms.  A fraction $p$ of individuals chooses the treatment in the Choice arm.  Finally, $D_i = Z_i\times \mathds{1}(Z_i\neq 2) + C_i\times \mathds{1}(Z_i=2)$ is the observed treatment indicator, and $Y(d,z)$ is the potential outcome function for $d=0,1$, and $z=0,1,2$.

%To test the difference between gains for choosers versus gains from non-choosers we need to identify $\mathbb{E}[Y_1-Y_0\;|\;C=1]$ (the Treatment on the Treated), and $\mathbb{E}[Y_1-Y_0\;|\;C=0]$ (the Treatment on the Untreated).   The observed outcome in the Choice arm is the weighted average of the treated and untreated outcomes; $p \times\mathbb{E}[Y_1\;|\;C=1] + (1-p)\times\mathbb{E}[Y_0\;|\;C=0]$.  Given assumptions a) and c) above we can recover the ToT from the difference between the Choice and Control arms as is standard, and then symmetrically we can invoke b) and c) to recover the TuT from the difference between the Forced and Choice arms as follows:

%\begin{align*}
%ToT \equiv \mathbb{E}[Y_1 - Y_0 \;\mid\; C=1]  &=   \frac{\mathbb{E}[Y \;\mid\; Z=2] - \mathbb{E}[Y \;\mid\; Z=0]}{p} \\
%TuT \equiv \mathbb{E}[Y_1 - Y_0 \;\mid \;C=0]  &=  \frac{\mathbb{E}[Y \;\mid\; Z=1] - \mathbb{E}[Y \;\mid\; Z=2]}{(1-p)} 
%\end{align*}

%This estimate of the ToT is the standard one that would result from instrumenting for compliance with the offering of treatment as in \cite{angrist1996identification}.  The TuT is the analogous estimator, which could be recovered in a regression pooling the forced and choice arms and instrumenting for \textit{not} complying with being assigned to the choice arm (for a more formal development, see the appendix).  The advantage of representing the estimands via division of the relevant ITT by the compliance (non-compliance) rate is that it allows us to estimate all the necessary terms from the single pooled regression Equation \ref{basic_reg}, from which the significance levels for the ToT, the TuT, and the difference between them can all be estimated as single-equation F-tests:

%\[ToT = \frac{\beta^C}{p}; \qquad\quad TuT = \frac{(\beta^F - \beta^C)}{(1-p)}; \qquad\quad (ToT-TuT) = \frac{\beta^C}{p}- \frac{(\beta^F - \beta^C)}{(1-p)}. \]

\todo[inline]{This next paragraph needs to be edited a bit. I think there's one more number that we need to put in the table of results: the SE for the ToT versus TuT?}

@@

\todo[inline]{Frank: cut this section.}

@@

\todo[inline]{Frank/Issac: need to discuss confidence interval construction for the mistakes exercise. I'm not 100\% sure about it. There's question of what we can actually infer from the random forest exercise. We can't learn the distribution of treatment effects within a ``bin'' but we can learn the ATE in the bin along with its standard error, and we can treat that as approximately normal. Another issue concerns whether we do or do not use the observed outcomes for the people in the choice arm. At present we're not using this. But you might say that we should. This would entail predicting their \emph{counterfactual} outcome. What I mean here is that $\text{ATE}(X)$ is what you would use to assign someone to a particular treatment, given that you have observed their $X$. But what we have is a little different. We observe both their $X$ and either $Y_1$ or $Y_0$. I think there's an interesting question here about whether we're interested in something \emph{ex ante} or \emph{ex post}. It relates to the issue of ``mistakes.'' We should discuss briefly as a group so Frank \& Issac can make the appropriate adjustments if needed.}

\todo[inline]{Issac: add in the picture for the ToT/TuT version of the ``mistakes'' exercise \& histograms of treatment effects by groups. We already have the histogram in figure 15 for the ATE. Is it possible to say something about the covariates of the choosers for whom we estimate a negative ToT?}

\todo[inline]{Frank draft: The first exercise looks at ``mistakes.'' These are defined by predicting treatment effects for the people in the \emph{choice} arm using their covariates. If the treatment effect is positive and they don't choose treatment, this is a mistake. If the treatment effect is negative and they choose treatment this is a mistake. There are two ways of carrying out this exercise. The first way assumes that, conditional on $X$, there is no selection on gains. This version uses a model of heterogeneous treatment effects estimated using only people from the forced arms to create predicted ATEs for people in the choice arm. The second version calculates ToT and TuT versions of the same thing, but this involves using data from the choice arm, so it's less efficient because sample-splitting is required so we have to discard some people from the choice arm when calculating ``mistakes.'' Issac implements this with 5 partitions of 20/80, repeating five times and averaging over the result. Comparing the results of the two versions we find something interesting. For the non-choosers, the results are similar in both versions. Lots of mistakes and pretty big. For the choosers, we find very little evidence of mistakes using the ATE version and much more using the ToT version. What does this mean? It suggests some form of perverse selection on gains. These must be people who think commitment will help them but it actually hurts them. Question: what are their covariates like? What kind of people are they? This gets to Craig's question about who is hurt in each treatment regime. There aren't very many choosers (only 11\%) and something between 15 and 35\%, depending on the threshold, of them are ``hurt'' according to our model. So quantitatively it's not many people. What about with the ATE: what fraction of people \emph{overall} do we predict are hurt by the treatment? (We bounded it above, but now we have a model.) Seems like this is around 1-2\%.}

@@

\begin{figure}[H]
    \caption{Fan \& Park bounds}
    \label{fan_park_bounds}
    \begin{center}
